Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-08 acl.2016/acl2016.tex
acl paper

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}
% If the title and author information does not fit in the area allocated,
% place \setlength\titlebox{<new height>} right after
% at the top, where <new height> can be something larger than 2.25in
\author{Hieu Hoang\\
	    Moses Machine Translation CIC\\
	    {\tt hieu@moses-mt.org}
	  \And
	Author 2\\
  	ABC University\\
  	900 Main Street\\
  	Ourcity, PQ, Canada A1A 1T2\\
  {\tt author2@abc.ca}}

@@

Overall though, the scalability is remarkably good, the decoder is able to make full use of all real and virtual cores. When all cores are saturated, the decoder is 16 times faster than single-threaded decoding, on this 16 real core server.

@@

more cores

We verify the results on a smaller French-English phrase-based model and test set container longer sentences. The speed gain is even greater than our main testing scenario, Figure~\ref{fig:fr-en-speed}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{fr-en-speed.png}} 
\end{tabular}
\caption{Decoding speed for fr-en model}
\label{fig:fr-en-speed}
\end{figure}

@@

>>>>

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}
% If the title and author information does not fit in the area allocated,
% place \setlength\titlebox{<new height>} right after
% at the top, where <new height> can be something larger than 2.25in
\author{Hieu Hoang\\
	    Moses Machine Translation CIC\\
	    {\tt hieu@moses-mt.org}
	  \And
	Nicolay Bogoychev\\
  	University of Edinburgh\\
  	10 Crichton Street\\
  	Edinburgh, Scotland, EH10 9AB\\
  {\tt s1031254@sms.ed.ac.uk}
	  \And
	Lane Schwartz\\
  	University of Illinois\\
  {\tt lanes@illinois.edu}
	  \AND
	Kenneth Heafield\\
  	University of Edinburgh\\
  {\tt kheafiel@inf.ed.ac.uk}
	  \And
	Marcin Junczys-Dowmunt\\
	Faculty of Mathematics and Computer Science \\
	Adam Mickiewicz University\\
  {\tt junczys@amu.edu.pl}
	}

@@

Overall though, the scalability is remarkably good, the decoder is able to make full use of all real and virtual cores. When all cores are saturated, the decoder is 16 times faster than single-threaded decoding, on this 16 real core server. It is also 4.5 times faster than Moses with a single-thread and 14.5 faster when all cores are used.

@@

??? more cores

We verify the results on a smaller French-English phrase-based model and test set container longer sentences. The speed gain is even greater than our main testing scenario, Figure~\ref{fig:fr-en-speed}. Our decoder is 5.4 times faster than Moses with a single-thread and 14.5 faster when all cores are saturated.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{fr-en-speed.png}} 
\end{tabular}
\caption{Decoding speed for fr-en model}
\label{fig:fr-en-speed}
\end{figure}

@@

We have presented a new decoder that is compatible with Moses. By studying the shortcomings of the current implementations, we are able to optimize for speed, especially for multicore operation. This has resulted in double digit gains compared to Moses on the same hardware. Our implementation is also unaffected by scalability issues that has afflicted Moses after 10-15 threads and continue to scale well for all possible cores we have tested it on.

In future, we shall work on exploring the underlying reasons for the scalability issues in Moses to get a better understanding where potential performance issues can arise. We shall also investigate other major components of the decoding algorithm, particulaly the language model which has not been touched in this paper.
